Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-01-10 Manuscript Analyses/manuscript_analysis.Rmd
updated effects plot function

  if (isFALSE(int)){
    dat %>%
      ggplot() +
      aes(x={{var}}, 
          y = .outcome) +
      geom_point() +
      geom_smooth(method = "lm")
  } else {
    dat %>%
      ggplot() +
      aes(x = {{var}},
          y= .outcome,
          group = cut_interval({{var2}}, num),
          color = cut_interval({{var2}}, num)) +
      geom_point() +
      geom_smooth(method = "lm") +
      theme(legend.position = "bottom")
  }
}

@@

effect_plot(mods2, list_sort_c, best_win) # Working Memory * Words in Noise Threshold
effect_plot(mods2, best_win, list_sort_c) # Words in Noise Threshold * Working Memory
effect_plot(mods2, best_win, int = F) # Words in Noise Threshold
effect_plot(mods2, list_sort_c, vocab_c) # Working Memory * Receptive Vocabulary
effect_plot(mods2, card_sort_c, pattern_c) # Cognitive Flexibility * Processing Speed
effect_plot(mods2, pattern_c, card_sort_c) # Processing Speed * Cognitive Flexibility
effect_plot(mods2, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
effect_plot(mods2, vocab_c, pattern_c) # Receptive Vocabulary * Processing Speed
effect_plot(mods2, pattern_c, vocab_c) # Processing Speed * Receptive Vocabulary
effect_plot(mods2, list_sort_c, card_sort_c) # Working Memory * Cognitive Flexibility
effect_plot(mods2, card_sort_c, list_sort_c) # Cognitive Flexibility * Working Memory

@@

effect_plot(mods22, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocabulary
effect_plot(mods22, vocab_c, card_sort_c) # Receptive Vocabulary * Cognitive Flexibility
effect_plot(mods22, flanker_c, pattern_c) # Inhibitory Control * Processing Speed
effect_plot(mods22, pattern_c, flanker_c) # Processing Speed * Inhibitory Control
effect_plot(mods22, vocab_c, int = F) # Receptive Vocab 
effect_plot(mods22, flanker_c, int = F) # Inhibitory Control
effect_plot(mods22, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
effect_plot(mods22, best_win, flanker_c) # Words in Noise Threshold * Inhibitory Control

>>>>

  if (isFALSE(int)){
    dat %>%
      ggplot() +
      aes(x={{var}}, 
          y = .outcome) +
      geom_point() +
      geom_smooth(method = "lm")
  } else {
    dat %>%
      ggplot() +
      aes(x = {{var}},
          y= .outcome,
          group = cut_number({{var2}}, num),
          color = cut_number({{var2}}, num)) +
      geom_point() +
      geom_smooth(method = "lm") +
      theme(legend.position = "bottom")
  }
}

@@

effect_plot(mods2, list_sort_c, best_win) # Working Memory * Words in Noise Threshold
#effect_plot(mods2, best_win, list_sort_c) # Words in Noise Threshold * Working Memory
effect_plot(mods2, best_win, int = F) # Words in Noise Threshold
effect_plot(mods2, list_sort_c, vocab_c) # Working Memory * Receptive Vocabulary
effect_plot(mods2, vocab_c, list_sort_c)
effect_plot(mods2, card_sort_c, pattern_c) # Cognitive Flexibility * Processing Speed
effect_plot(mods2, pattern_c, card_sort_c) # Processing Speed * Cognitive Flexibility
effect_plot(mods2, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
effect_plot(mods2, vocab_c, pattern_c) # Receptive Vocabulary * Processing Speed
effect_plot(mods2, pattern_c, vocab_c) # Processing Speed * Receptive Vocabulary
effect_plot(mods2, list_sort_c, card_sort_c) # Working Memory * Cognitive Flexibility
effect_plot(mods2, card_sort_c, list_sort_c) # Cognitive Flexibility * Working Memory

@@

# effect_plot(mods22, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocabulary
effect_plot(mods22, vocab_c, card_sort_c) # Receptive Vocabulary * Cognitive Flexibility
effect_plot(mods22, flanker_c, pattern_c) # Inhibitory Control * Processing Speed
effect_plot(mods22, pattern_c, flanker_c) # Processing Speed * Inhibitory Control
effect_plot(mods22, vocab_c, int = F) # Receptive Vocab 
effect_plot(mods22, flanker_c, int = F) # Inhibitory Control
effect_plot(mods22, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
effect_plot(mods22, best_win, flanker_c) # Words in Noise Threshold * Inhibitory Control
